\documentclass[12pt, a4paper]{article}
\usepackage[french]{babel}
\usepackage{caption}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{geometry}
\usepackage{pgfplots}

\usepgfplotslibrary{polar}
\pgfplotsset{compat=1.12} 

\pgfplotsset{width=10cm,compat=1.9}
\usepackage[colorlinks=true,linkcolor=black,anchorcolor=black,citecolor=black,filecolor=black,menucolor=black,runcolor=black,urlcolor=black]{hyperref}
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{}
\rhead{}
\chead{}
\rfoot{\thepage}
\lfoot{Martin Baumgaertner -- Mikhaïl Karapetyan -- Louis Pluviose -- Nicolas Wagner -- Thomas Strub -- Victor Uettwiller}
\cfoot{}

\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\begin{document}
\begin{titlepage}
	\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} 
	\center 
	\textsc{\LARGE iut of colmar}\\[6.5cm] 
	\textsc{\Large SAE 5.02 piloter un projet informatique}\\[0.5cm] 
	\textsc{\large year 2023-24}\\[0.5cm]
	\HRule\\[0.75cm]
	{\Large\bfseries Tasko - Report on Our Project}\\[0.4cm]
	\HRule\\[0.5cm]
	\textsc{\large martin baumgaertner - mikhaïl karapetyan\\louis pluviose - nicolas wagner\\thomas strub - victor uettwiller}\\[6cm] 

	\vfill\vfill\vfill
	{\large\today} 
	\vfill
\end{titlepage}
\newpage
\tableofcontents
\listoffigures
\newpage
\section{Introduction}
In today's fast-paced and collaborative work 
environments, effective task management is paramount 
to productivity and project success. "Tasko," a 
robust and user-friendly task management application, 
has been developed by a dedicated team of six talented 
individuals to meet the growing demands of modern task 
management. This report provides an in-depth analysis 
of Tasko, it's key features, and how it empowers users 
to effortlessly manage their tasks and projects. From 
task creation and assignment to online data backup and 
Docker deployment, Tasko offers a comprehensive 
solution for individuals and teams striving to enhance 
productivity and streamline collaboration. This 
report will delve into the core functionalities of 
Tasko, shedding light on its potential to revolutionize 
the way we organize, track, and accomplish our tasks.

\subsection{Features}
Tasko offers a comprehensive set of features designed 
to streamline task and subtask management while 
enhancing collaboration and productivity. Users 
can effortlessly create, organize, and track 
tasks and subtasks to simplify even the most 
complex projects. Task assignment capabilities 
promote effective teamwork and accountability, 
making it easy to delegate responsibilities. 
Online backup options, including Git repositories 
and web servers, ensure that your data remains 
secure and accessible, providing peace of mind. 
Deadlines and due dates can be set to efficiently 
manage tasks and meet project goals, while the 
prioritization feature enables users to focus on 
what matters most and stay on top of their workloads. 
Customizable labels allow for quick task categorization 
and easy identification. Furthermore, Docker deployment 
simplifies Tasko setup, providing a hassle-free and 
consistent environment for users.

\section{Organization}
Swiftly, the need for effective organization
became evident as we embarked on the journey of
creating our project. It was at this point that I
stepped forward to take on the role of Product
Owner. My fellow team members graciously accepted
my offer, recognizing my diplomatic nature and
strong communication skills as valuable assets
for this role. Subsequently, Thomas expressed
his eagerness to assume the position of Scrum
Master. With these key roles defined, we proceeded
to divide the project into several distinct parts.
These segments encompassed the backend and database
development, frontend design, Docker/container
implementation, documentation, and the creation
of web HTML elements. Thomas, along with Mikhail
and Nicolas, took charge of the web HTML/frontend
portion, while Louis spearheaded the backend and
database aspects. Victor assumed responsibility
for the infrastructure related to Docker containers,
while I adopted a versatile role, lending assistance
wherever needed and primarily focusing on documentation.
The allocation of these roles was carefully considered
by the group members to foster harmonious collaboration
and to prevent disagreement.

\end{document}